\name: Combining Bottom-up and top-down approaches through graph learning over interaction networks for drug-target-interaction prediction

### 2021-02-07 paper/main.tex
Results restructuring

We trained, validated and finally tested all considered models on the
STITCH dataset using a 5-fold cross-validation over a protein
split; we then selected the best-performing models (with respect to
\textit{AUROC} and $MicroAUC_p$) and evaluate them on the Yamanishi
benchmark dataset.

We will hereby denote the molecular feature based predictor with \textit{MolPred}, while abbreviating the ontology based, top-down predictor with \textit{OntoPred}. As depicted in Figure \ref{tab:STITCHresults}, \textit{OntoPred} is showing significantly better performance on STITCH, while also only \textit{OntoPred} shows significant performance increase when adding \textit{GENConv} graph convolutional neural layers over the PPI graph. However, graph convolutional neural layers such as \textit{GCNConv} and \textit{GENConv}, especially when incorporated into the proposed \textit{ResGraphConv} blocks, add a lot of learnable parameters to the network, leading to more expressive power. This may lead to better performance, while deceiving, whether the respective features actually localize on the PPI graph.

>>>>

We trained, validated and finally tested all considered models on the
STITCH dataset using a 5-fold cross-validation over a protein
split; we then selected the best-performing models (with respect to
\textit{AUROC} and $MicroAUC_p$) and evaluate them on the Yamanishi
benchmark dataset. To evaluate the influence of the different
features separately, and determine whether they ``localize'' on the
PPI graph (and therefore can be exploited successfully by the graph
neural networks), we train and evaluate models with different types of
features, and with and without inclusion of the PPI graph,
separately.
Table \ref{tab:STITCHresults} shows the results.

\todo[inline]{Move to caption of table.}
We will hereby denote the molecular feature based predictor with
\textit{MolPred}, while abbreviating the ontology based, top-down
predictor with \textit{OntoPred}.

We find that the model using ontology-based features
(\textit{OntoPred}) is showing significantly\todo{significance test
  and p value? otherwise remove} better performance on STITCH compared
to using only molecular features. We also observe that only the model
using ontology-based features results in significantly\todo{p-val}
increased performance when incorporating the PPI graph, demonstrating
that these features localize on the PPI network whereas the molecular
features do not.

, while also only \textit{OntoPred} shows significant performance increase when adding \textit{GENConv} graph convolutional neural layers over the PPI graph. However, graph convolutional neural layers such as \textit{GCNConv} and \textit{GENConv}, especially when incorporated into the proposed \textit{ResGraphConv} blocks, add a lot of learnable parameters to the network, leading to more expressive power. This may lead to better performance, while deceiving, whether the respective features actually localize on the PPI graph.
